---
title: "FA 541 Assignment4"
author: "Jiawei Lu  Yucan Li"
date: "10/6/2021"
output: html_document
---
Found 15 stocks from 15 different sectors in other to minimize the covariance between each other’s. The Market capitalization of each selected stock is located in the top three of its respective sectors. The mean-variance model is then used to calculate the optimal ratio between each stock. The train period is from 2019-01-01 to 2021-03-30. The test period is from 2021-04-01 to 2021-09-30. Finally, the returns, volatilities and sharpe ratios are calculated in comparison to the S&P 500, Nasdaq index and Dow Jones Industrial Average.  

Selected sectors: COMMERCIAL SERVICES, COMMUNICATIONS, CONSUMER, DISTRIBUTION SERVICES, ELECTRONIC TECHNOLOGY, ENERGY MINERALS, FINANCE, HEALTH, INDUSTRIAL SERVICES, PROCESS INDUSTRIES, PRODUCER MANUFACTURING, RETAIL TRADE, TECHNOLOGY SERVICES, TRANSPORTATION, UTILITIES.  
Reference : https://www.tradingview.com/markets/stocks-usa/sectorandindustry-sector/  

```{r}
library(quantmod)
library(xts)
set.seed(100)

p1=get(getSymbols("MCO",from="2018-01-01",to="2021-03-30"))
pMCO<- p1[,6]
p2=get(getSymbols("VZ",from="2018-01-01",to="2021-03-30"))
pKORE <- p2[,6]
p3=get(getSymbols("TSLA",from="2018-01-01",to="2021-03-30"))
pTSLA <- p3[,6]
p4=get(getSymbols("SYY",from="2018-01-01",to="2021-03-30"))
pSYY <- p4[,6]
p5=get(getSymbols("AAPL",from="2018-01-01",to="2021-03-30"))
pAAPL <- p5[,6]
p6=get(getSymbols("XOM",from="2018-01-01",to="2021-03-30"))
pXOM <- p6[,6]
p7=get(getSymbols("JPM",from="2018-01-01",to="2021-03-30"))
pJPM <- p7[,6]
p8=get(getSymbols("UNH",from="2018-01-01",to="2021-03-30"))
pUNH <- p8[,6]

p9=get(getSymbols("ENB",from="2018-01-01",to="2021-03-30"))
pENB <- p9[,6]


p10=get(getSymbols("LIN",from="2018-01-01",to="2021-03-30"))
pLIN <- p10[,6]

p11=get(getSymbols("ASML",from="2018-01-01",to="2021-03-30"))
pASML <- p11[,6]

p12=get(getSymbols("AMZN",from="2018-01-01",to="2021-03-30"))
pAMZN <- p12[,6]

p13=get(getSymbols("MSFT",from="2018-01-01",to="2021-03-30"))
pMSFT <- p13[,6]

p14=get(getSymbols("UPS",from="2018-01-01",to="2021-03-30"))
pUPS <- p14[,6]

p15=get(getSymbols("NEE",from="2018-01-01",to="2021-03-30"))
pNEE <- p15[,6]


sp500 <- new.env()

p16 <- getSymbols("^GSPC", src = "yahoo",from = as.Date("2018-01-01"), to = as.Date("2021-03-30"))


p17= getSymbols("^IXIC", src = "yahoo",from = as.Date("2018-01-01"), to = as.Date("2021-03-30"))


p18 =getSymbols("^DJI", src = "yahoo",from = as.Date("2018-01-01"), to = as.Date("2021-03-30"))



plot(Ad(GSPC))
plot(Ad(IXIC))
plot(Ad(DJI))

price<-cbind(pMCO,pKORE,pTSLA,pSYY,pAAPL,pXOM,pJPM,pUNH,pENB,pLIN,pASML,pAMZN,pMSFT,pUPS,pNEE)
plot(price)
summary(price)

return<-na.omit(log(price/lag(price)))

length(names(return))
# Compute a correlation matrix
corr <- round(cor(return), 1)
head(corr[, 1:15])

library(ggcorrplot)
ggcorrplot(corr)
```

```{r}
library(tidyquant) # To download the data
library(plotly) # To create interactive charts
library(timetk) # To manipulate the data series
library(tibble)
library(dplyr)

tick = names(return)
wts <- runif(n = length(tick))
print(wts)
print(sum(wts))
wts <- wts/sum(wts)
print(wts)
sum(wts)

mean_ret <- colMeans(return)
print(round(mean_ret, 5))
port_returns <- (sum(wts * mean_ret) + 1)^252 - 1
port_returns

cov_mat <- cov(return) * 252

port_risk <- sqrt(t(wts) %*% (cov_mat %*% wts))
print(port_risk)

# Since Risk free rate is 0.0053/25% 
sharpe_ratio <- (port_returns-0.0053/2)/port_risk
print(sharpe_ratio)


# Calculate the random weights
wts <- runif(n = length(tick))
wts <- wts/sum(wts)

# Calculate the portfolio returns
port_returns <- (sum(wts * mean_ret) + 1)^252 - 1

# Calculate the portfolio risk
port_risk <- sqrt(t(wts) %*% (cov_mat %*% wts))

# Calculate the Sharpe Ratio
sharpe_ratio <- port_returns/port_risk

print(wts)
```

```{r}
num_port <- 100000

# Creating a matrix to store the weights

all_wts <- matrix(nrow = num_port,
                  ncol = length(tick))

# Creating an empty vector to store
# Portfolio returns

port_returns <- vector('numeric', length = num_port)

# Creating an empty vector to store
# Portfolio Standard deviation

port_risk <- vector('numeric', length = num_port)

# Creating an empty vector to store
# Portfolio Sharpe Ratio

sharpe_ratio <- vector('numeric', length = num_port)
```

```{r}
for (i in seq_along(port_returns)) {
  
  wts <- runif(length(tick))
  wts <- wts/sum(wts)
  
  # Storing weight in the matrix
  all_wts[i,] <- wts
  
  # Portfolio returns
  
  port_ret <- sum(wts * mean_ret)
  port_ret <- ((port_ret + 1)^252) - 1
  
  # Storing Portfolio Returns values
  port_returns[i] <- port_ret
  
  
  # Creating and storing portfolio risk
  port_sd <- sqrt(t(wts) %*% (cov_mat  %*% wts))
  port_risk[i] <- port_sd
  
  # Creating and storing Portfolio Sharpe Ratios
  # Assuming 0% Risk free rate
  
  sr <- (port_ret-0.0053/2)/port_sd
  sharpe_ratio[i] <- sr
  
}
```

```{r}
# Storing the values in the table
portfolio_values <- tibble(Return = port_returns,
                  Risk = port_risk,
                  SharpeRatio = sharpe_ratio)


# Converting matrix to a tibble and changing column names
all_wts <- tk_tbl(all_wts)
```

```{r}
colnames(all_wts) <- colnames(return)

# Combing all the values together
portfolio_values <- tk_tbl(cbind(all_wts, portfolio_values))
```

```{r}
head(portfolio_values)
```

```{r}
#min_var <- portfolio_values[which.min(portfolio_values$Risk),]
max_sr <- portfolio_values[which.max(portfolio_values$SharpeRatio),]
```

```{r}
library(tidyr)
a = c()
for (i in max_sr[1:15]){
 a =c(a,i)
}
sum(a)
as.list(max_sr)

library(data.table)
data = as.data.frame(t(t(return) * a))
data$sum = rowSums(data)

f = read.csv("ff.csv")

colnames(f) <- c("Date", "Mkt.Rf", "SMB", "HML", "Rf")

library(lubridate)

f$Date <- ymd(f$Date)
df = cbind(data,f)
df$fundX = (df$sum - df$Rf)*100
```

```{r}
#data2  = xts(data$sum, order.by=index(data))
plot(x = index(data), y = data$sum, type = "l", main = "Portfolio Daily Returns")
plot(cumsum(data$sum), type = "l", main = "Portfolio Cumulative Returns")
```


```{r}
market_return1 <- na.omit(diff(log(Ad(GSPC)), lag=1))
#tibble_as_list(max_sr[1:15])
#sum(port_returns * 2 * as.list(max_sr)[16:])

GSPC = (market_return1-df$Rf)*100
summary(lm(df$fundX~ GSPC ))

GSPC = as.matrix(GSPC)
plot(GSPC ,df$fundX)
abline(lm(df$fundX~GSPC))
```

```{r}
market_return2 <- na.omit(diff(log(Ad(IXIC)), lag=1))

IXIC = (market_return2-df$Rf)*100

summary(lm(df$fundX~IXIC))

IXIC = as.matrix(IXIC)
plot(IXIC,df$fundX)
abline(lm(df$fundX~IXIC))
```

```{r}
market_return3 <- na.omit(diff(log(Ad(DJI)), lag=1))

DJI = (market_return3-df$Rf)*100

summary(lm(df$fundX~DJI))

DJI = as.matrix(DJI)
plot(DJI,df$fundX)
abline(lm(df$fundX~DJI))
```
`

```{r}
#market_return1 <- na.omit(diff(log(Ad(GSPC)), lag=1))
#tibble_as_list(max_sr[1:15])
#sum(port_returns * 2 * as.list(max_sr)[16:])

#Market_Risk_Premium = 100*market_return1-0.0053

model = lm(df$fundX~ df$SMB + df$HML + GSPC)
summary(lm(df$fundX~ df$SMB + df$HML + GSPC))

plot(cumsum(df$sum*100), type = "l", main = "Portfolio Cumulative Returns")
model
```

```{r}
#"2018-01-01",to="2021-03-30"
#lines(as.ts(cumsum(df$SMB)))
plot(as.ts(df$SMB), main=NA, ylim=c(-15,15),col='black')
lines(as.ts(df$HML),col="red")
lines(as.ts(df$Mkt.Rf),col='green')
lines(as.ts(df$Rf),col='blue')
legend(0, 15, legend=c("SMB", "HML", "Mkt-Rf","Rf"), 
       col=c('black', 'red','green','blue'), lty=1)
mtext(text="Fama/French Factors from K. French", 
      adj=0, outer=T, line=-2, cex=1.5)
head(df)
```

```{r}
plot(as.ts((cumsum(df$sum)*100-df$Rf*100)), main=NA, ylim=c(-70,120),col='black')
lines(as.ts(cumsum(market_return1)*100+df$Rf*100),col="red")
legend(0, 48, legend=c("Weight Portfolio", "Market index"), 
       col=c('black', 'red'), lty=1)
mtext(text="Fama/French Factors from K. French", 
      adj=0, outer=T, line=-2, cex=1.5)

```

```{r}
plot(as.ts((cumsum(df$sum)*100-df$Rf*100)), main=NA, ylim=c(-70,120),col='black')
lines(as.ts(cumsum(market_return2)*100+df$Rf*100),col="red")
legend(0, 48, legend=c("Weight Portfolio", "Market index"), 
       col=c('black', 'red'), lty=1)
mtext(text="Fama/French Factors from K. French", 
      adj=0, outer=T, line=-2, cex=1.5)
```

```{r}
plot(as.ts((cumsum(df$sum)*100-df$Rf*100)), main=NA, ylim=c(-70,120),col='black')
lines(as.ts(cumsum(market_return3)*100+df$Rf*100),col="red")
legend(0, 48, legend=c("Weight Portfolio", "Market index"), 
       col=c('black', 'red'), lty=1)
mtext(text="Fama/French Factors from K. French", 
      adj=0, outer=T, line=-2, cex=1.5)
```

```{r}
table = data.frame(alpha=coef(model)["(Intercept)"],beta =coef(model)["GSPC"],sharpe_ratio = max_sr$SharpeRatio,return = max_sr$Return, risk = max_sr$Risk)
rownames(table) = "values"
table

```

